STA107 Post-Course Survey Analysis

### 2025-04-14 paper/paper.tex
Added Qual changes for themes

\usepackage{color}
\usepackage{fancyvrb}
\newcommand{\VerbBar}{|}
\newcommand{\VERB}{\Verb[commandchars=\\\{\}]}
\DefineVerbatimEnvironment{Highlighting}{Verbatim}{commandchars=\\\{\}}
% Add ',fontsize=\small' for more characters per line
\usepackage{framed}
\definecolor{shadecolor}{RGB}{241,243,245}
\newenvironment{Shaded}{\begin{snugshade}}{\end{snugshade}}
\newcommand{\AlertTok}[1]{\textcolor[rgb]{0.68,0.00,0.00}{#1}}
\newcommand{\AnnotationTok}[1]{\textcolor[rgb]{0.37,0.37,0.37}{#1}}
\newcommand{\AttributeTok}[1]{\textcolor[rgb]{0.40,0.45,0.13}{#1}}
\newcommand{\BaseNTok}[1]{\textcolor[rgb]{0.68,0.00,0.00}{#1}}
\newcommand{\BuiltInTok}[1]{\textcolor[rgb]{0.00,0.23,0.31}{#1}}
\newcommand{\CharTok}[1]{\textcolor[rgb]{0.13,0.47,0.30}{#1}}
\newcommand{\CommentTok}[1]{\textcolor[rgb]{0.37,0.37,0.37}{#1}}
\newcommand{\CommentVarTok}[1]{\textcolor[rgb]{0.37,0.37,0.37}{\textit{#1}}}
\newcommand{\ConstantTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{#1}}
\newcommand{\ControlFlowTok}[1]{\textcolor[rgb]{0.00,0.23,0.31}{\textbf{#1}}}
\newcommand{\DataTypeTok}[1]{\textcolor[rgb]{0.68,0.00,0.00}{#1}}
\newcommand{\DecValTok}[1]{\textcolor[rgb]{0.68,0.00,0.00}{#1}}
\newcommand{\DocumentationTok}[1]{\textcolor[rgb]{0.37,0.37,0.37}{\textit{#1}}}
\newcommand{\ErrorTok}[1]{\textcolor[rgb]{0.68,0.00,0.00}{#1}}
\newcommand{\ExtensionTok}[1]{\textcolor[rgb]{0.00,0.23,0.31}{#1}}
\newcommand{\FloatTok}[1]{\textcolor[rgb]{0.68,0.00,0.00}{#1}}
\newcommand{\FunctionTok}[1]{\textcolor[rgb]{0.28,0.35,0.67}{#1}}
\newcommand{\ImportTok}[1]{\textcolor[rgb]{0.00,0.46,0.62}{#1}}
\newcommand{\InformationTok}[1]{\textcolor[rgb]{0.37,0.37,0.37}{#1}}
\newcommand{\KeywordTok}[1]{\textcolor[rgb]{0.00,0.23,0.31}{\textbf{#1}}}
\newcommand{\NormalTok}[1]{\textcolor[rgb]{0.00,0.23,0.31}{#1}}
\newcommand{\OperatorTok}[1]{\textcolor[rgb]{0.37,0.37,0.37}{#1}}
\newcommand{\OtherTok}[1]{\textcolor[rgb]{0.00,0.23,0.31}{#1}}
\newcommand{\PreprocessorTok}[1]{\textcolor[rgb]{0.68,0.00,0.00}{#1}}
\newcommand{\RegionMarkerTok}[1]{\textcolor[rgb]{0.00,0.23,0.31}{#1}}
\newcommand{\SpecialCharTok}[1]{\textcolor[rgb]{0.37,0.37,0.37}{#1}}
\newcommand{\SpecialStringTok}[1]{\textcolor[rgb]{0.13,0.47,0.30}{#1}}
\newcommand{\StringTok}[1]{\textcolor[rgb]{0.13,0.47,0.30}{#1}}
\newcommand{\VariableTok}[1]{\textcolor[rgb]{0.07,0.07,0.07}{#1}}
\newcommand{\VerbatimStringTok}[1]{\textcolor[rgb]{0.13,0.47,0.30}{#1}}
\newcommand{\WarningTok}[1]{\textcolor[rgb]{0.37,0.37,0.37}{\textit{#1}}}

@@

\subsubsection{Qualitative Analysis}\label{qualitative-analysis}

\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{\# Load required libraries}
\FunctionTok{library}\NormalTok{(tidyverse)}
\FunctionTok{library}\NormalTok{(stringr)}
\FunctionTok{library}\NormalTok{(tidytext)}
\FunctionTok{library}\NormalTok{(syuzhet)}
\FunctionTok{library}\NormalTok{(ggplot2)}
\FunctionTok{library}\NormalTok{(tidyr)}
\FunctionTok{library}\NormalTok{(wordcloud)}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
Loading required package: RColorBrewer
\end{verbatim}

\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{\# Read in the survey data}
\NormalTok{data }\OtherTok{\textless{}{-}}\NormalTok{ qualitative\_data}

\CommentTok{\# Rename columns}
\FunctionTok{colnames}\NormalTok{(data)[}\DecValTok{1}\SpecialCharTok{:}\DecValTok{11}\NormalTok{] }\OtherTok{\textless{}{-}} \FunctionTok{c}\NormalTok{(}\StringTok{"Q3"}\NormalTok{, }\StringTok{"Q6"}\NormalTok{, }\StringTok{"Q8"}\NormalTok{, }\StringTok{"Q10"}\NormalTok{, }\StringTok{"Q11"}\NormalTok{, }
                          \StringTok{"Q12"}\NormalTok{, }\StringTok{"Q13"}\NormalTok{, }\StringTok{"Q14"}\NormalTok{, }\StringTok{"Q15"}\NormalTok{, }\StringTok{"Q16"}\NormalTok{, }\StringTok{"Q17"}\NormalTok{)}

\CommentTok{\# Clean the text}
\NormalTok{data\_clean }\OtherTok{\textless{}{-}}\NormalTok{ data }\SpecialCharTok{\%\textgreater{}\%}
  \FunctionTok{mutate}\NormalTok{(}\FunctionTok{across}\NormalTok{(}\FunctionTok{everything}\NormalTok{(), }\SpecialCharTok{\textasciitilde{}} \FunctionTok{str\_trim}\NormalTok{(}\FunctionTok{tolower}\NormalTok{(}\FunctionTok{as.character}\NormalTok{(.)))))}

\CommentTok{\# Initialize an empty data frame to collect sentiment results}
\NormalTok{sentiment\_results }\OtherTok{\textless{}{-}} \FunctionTok{data.frame}\NormalTok{(}
  \AttributeTok{Question =} \FunctionTok{character}\NormalTok{(),}
  \AttributeTok{Positive =} \FunctionTok{numeric}\NormalTok{(),}
  \AttributeTok{Negative =} \FunctionTok{numeric}\NormalTok{(),}
  \AttributeTok{Neutral =} \FunctionTok{numeric}\NormalTok{(),}
  \AttributeTok{stringsAsFactors =} \ConstantTok{FALSE}
\NormalTok{)}

\CommentTok{\# Function to calculate sentiment}
\NormalTok{analyze\_sentiment }\OtherTok{\textless{}{-}} \ControlFlowTok{function}\NormalTok{(question\_col, question\_name) \{}
\NormalTok{  sentiments }\OtherTok{\textless{}{-}} \FunctionTok{get\_nrc\_sentiment}\NormalTok{(data\_clean[[question\_col]])}

\NormalTok{  pos }\OtherTok{\textless{}{-}} \FunctionTok{sum}\NormalTok{(sentiments}\SpecialCharTok{$}\NormalTok{positive)}
\NormalTok{  neg }\OtherTok{\textless{}{-}} \FunctionTok{sum}\NormalTok{(sentiments}\SpecialCharTok{$}\NormalTok{negative)}
\NormalTok{  neutral }\OtherTok{\textless{}{-}} \FunctionTok{nrow}\NormalTok{(sentiments) }\SpecialCharTok{{-}} 
    \FunctionTok{sum}\NormalTok{(}\FunctionTok{rowSums}\NormalTok{(sentiments[, }\FunctionTok{c}\NormalTok{(}\StringTok{"positive"}\NormalTok{, }\StringTok{"negative"}\NormalTok{)]) }\SpecialCharTok{\textgreater{}} \DecValTok{0}\NormalTok{)}

\NormalTok{  sentiment\_results }\OtherTok{\textless{}\textless{}{-}} \FunctionTok{rbind}\NormalTok{(sentiment\_results, }\FunctionTok{data.frame}\NormalTok{(}
    \AttributeTok{Question =}\NormalTok{ question\_name,}
    \AttributeTok{Positive =}\NormalTok{ pos,}
    \AttributeTok{Negative =}\NormalTok{ neg,}
    \AttributeTok{Neutral =}\NormalTok{ neutral}
\NormalTok{  ))}
\NormalTok{\}}

\CommentTok{\# Apply the function to all relevant questions}
\NormalTok{question\_names }\OtherTok{\textless{}{-}} \FunctionTok{c}\NormalTok{(}\StringTok{"Q3"}\NormalTok{, }\StringTok{"Q6"}\NormalTok{, }\StringTok{"Q8"}\NormalTok{, }\StringTok{"Q10"}\NormalTok{, }\StringTok{"Q11"}\NormalTok{, }
                    \StringTok{"Q12"}\NormalTok{, }\StringTok{"Q13"}\NormalTok{, }\StringTok{"Q14"}\NormalTok{, }\StringTok{"Q15"}\NormalTok{, }\StringTok{"Q16"}\NormalTok{, }\StringTok{"Q17"}\NormalTok{)}

\ControlFlowTok{for}\NormalTok{ (qn }\ControlFlowTok{in}\NormalTok{ question\_names) \{}
  \FunctionTok{analyze\_sentiment}\NormalTok{(qn, qn)}
\NormalTok{\}}
\end{Highlighting}
\end{Shaded}

@@

\begin{itemize}
\tightlist
\item
  Distribution of responses to Likert-scale questions
\item
  Summary statistics (mean, median, SD)
\item
  Visualizations: bar plots, histograms
\end{itemize}

>>>>

@@

\subsection{Quantitative Analysis}\label{quantitative-analysis}

\subsubsection{Communication Ability Before
vs.~After}\label{communication-ability-before-vs.-after}

\includegraphics{paper_files/figure-pdf/unnamed-chunk-3-1.pdf}

The histogram shows a clear improvement in students' perceived
communication ability. More students rated themselves at level 4 or 5
after the course compared to before, indicating that the course helped
them gain confidence in articulating statistical ideas.

\subsubsection{R Ability Before
vs.~After}\label{r-ability-before-vs.-after}

\includegraphics{paper_files/figure-pdf/unnamed-chunk-4-1.pdf}

Students entered the course with relatively low self-reported R skills
(mostly 1s and 2s), but after completing the course, a majority rated
themselves at 3 or higher. This shift demonstrates the course's success
in introducing R programming effectively.

\subsubsection{Understanding After Assignments
vs.~Tutorials}\label{understanding-after-assignments-vs.-tutorials}

\includegraphics{paper_files/figure-pdf/unnamed-chunk-5-1.pdf}

Students found both tutorials and assignments useful for understanding
statistical concepts, with a slight preference for tutorials. The higher
number of level 4 and 5 responses for tutorials suggests that real-time,
interactive support may have been especially beneficial.

\subsection{Qualitative Analysis}\label{qualitative-analysis}

@@

The survey included six Likert-scale questions aimed at capturing
students' self-perceived development in statistical understanding and
communication, both before and after the course. The questions also
addressed students' ability to use R software and their comprehension of
statistical concepts through tutorials and weekly assignments.

Key findings include:

\begin{itemize}
\tightlist
\item
  \textbf{Improved Communication Skills}: Students reported a notable
  improvement in their ability to communicate statistics, with the
  average post-course rating (M = 3.92) higher than the pre-course
  rating (M = 3.09).
\item
  \textbf{Increased R Proficiency}: The mean rating for R software usage
  rose from 2.43 before the course to 3.49 after completing it,
  indicating significant growth in computational skills.
\item
  \textbf{Conceptual Understanding}: Understanding of statistical
  concepts improved through both tutorials (M = 4.09) and weekly
  assignments (M = 3.84), with tutorials being rated slightly more
  helpful on average.
\end{itemize}

The graphs above illustrate the distribution of responses across the
three themes: communication, R proficiency, and statistical
understanding.
